---
title: "Economic Thinking"
output: 
  learnr::tutorial:
    progressive: true
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(mosaic)
TableTennis <- read.csv2("TableTennis.csv")
```

## Bat and ball

A bat and ball cost 1,10 Euro.
If the bat costs 1 Euro more than the ball.

```{r einstieg, echo=FALSE}
question(" What does the ball cost?",
  answer("5 Cent.", correct = TRUE, message = "0.05 + (0.05 + 1.00) = 1.10"),
  answer("10 Cent.", message = "0.05 + (0.05 + 1.00) = 1.10"),
  answer("1 Euro.", message = "0.05 + (0.05 + 1.00) = 1.10"),
  answer("Can not tell.", message = "0.05 + (0.05 + 1.00) = 1.10")
  )
```


##

What do you think: how many students can answer this question correctly?

##

Accoring to a [survey of the university of Bonn and the newspaper DIE ZEIT](https://www.zeit.de/wirtschaft/2018-02/oekonomie-wissen-wirtschaft-deutschen-studie)) $11\%$ gave the correct answer (*5 Cent*).

##

Were FOM students better?

## Preliminaries

Load package `mosaic`:

```{r mosaic}
library(mosaic)
```

Read in data of the (convinient) sample of FOM students:

```{r read.csv2}
TableTennis <- read.csv2("TableTennis.csv")
```

First view:

```{r RL}
TableTennis
```


## Analysis economic thinking

Univariate Analysis of categorical data via `mosaic`:

- Bargraph `gf_bar( ~ my.x, data = My.Data)`
- Table `tally( ~ my.x, data = My.Data)`
- Proportion `prop( ~ my.x, success = "my.success", data = My.Data)`

Analyze accordingly:

```{r Auswertung, exercise = TRUE, eval=FALSE}
___( ~ Price_Ball, data = TableTennis)
```

```{r Auswertung-solution}
gf_bar( ~ Price_Ball, data = TableTennis)
tally( ~ Price_Ball, data = TableTennis)
prop( ~ Price_Ball, success = "5 Cent.", data = TableTennis)
```

##

With $p=`r round(prop( ~ Price_Ball, success = "5 Cent.", data = TableTennis),2)`$ the correct proportion is higher than in the survey of DIE ZEIT ($\approx 11\%$).

##

With the alternatives:

- 5 Cent.
- 10 Cent.
- 1 Euro.
- Can not tell.

probability 

```{r raten, echo=FALSE}
question(" What is the probability of answering correctly by chance?",
  answer("0%", message = "One out of four is correct."),
  answer("25%", correct = TRUE, message = "One out of four is correct."),
  answer("50%", message = "One out of four is correct."),
  answer("100%", message = "One out of four is correct.")
  )
```


## Outlook

In *Inferential Statistics* we are analyzing the propability of getting `r tally( ~ Price_Ball, data = TableTennis)[3]` from `r sum(tally( ~ Price_Ball, data = TableTennis))` (i. e. $p=\frac{`r tally( ~ Price_Ball, data = TableTennis)[3]`}{`r sum(tally( ~ Price_Ball, data = TableTennis))`}=`r round(prop( ~ Price_Ball, success = "5 Cent.", data = TableTennis),2)`$) correctly, if students were guessing (i. e. $\pi=\frac{1}{4}=`r round(1/4,2)`$).
